### 2015-11-11 postdoctoral/S_prime_kappa.tex
add topological stuff

@@

  \begin{theorem}
    Figure \ref{GamesDiagram2} holds. (Proven in [TODO cite])
  \end{theorem}

@@

    Let \(\<C_0,C_1,\dots\>\) be an attack by
    \(\pl C\) in \(\schFillIntGame{\omega_\alpha}\), and
    \(\alpha\in\bigcap_{n<\omega}C_n\).
    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
    attack
    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
    by \(\pl C\) in \(\schFillIntGame{\omega_{\beta_{N+1}}}\). Since
    \(\sigma_{N+1}\) is a winning strategy and
    \(\alpha\in\bigcap_{n<\omega}C_{N+n+1}\cap\omega_{\beta_{N+1}}\), either
    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
    \(
      \alpha
        \in
      \sigma_{N+1}(
        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
        ,M+1
      )
    \)
    for some \(M<\omega\) and thus
    \(
      \alpha
        \in
      \sigma(
        \<C_{N+M+1},C_{N+M+2}\>,
        N+M+2
      )
    \). Thus \(\sigma\) is a winning strategy.
  \end{proof}
\end{document}

>>>>

  \begin{question}
    Is \(S'(\theta)\) equivalent to having a Kurepa family on \(\theta\)?
  \end{question}

@@

  \begin{theorem}
    Figure \ref{GamesDiagram2} holds. (Proven in [TODO cite])
    (Actually, TODO double-check that it works with just S', particularly
    the strict game)
  \end{theorem}

@@

    Let \(\<C_0,C_1,\dots\>\) be an attack by
    \(\pl C\) in \(\schFillIntGame{\omega_\alpha}\), and
    \(\alpha\in\bigcap_{n<\omega}C_n\).
    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
    attack
    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
    by \(\pl C\) in \(\schFillIntGame{\omega_{\beta_{N+1}}}\). Since
    \(\sigma_{N+1}\) is a winning strategy and
    \(\alpha\in\bigcap_{n<\omega}C_{N+n+1}\cap\omega_{\beta_{N+1}}\), either
    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
    \(
      \alpha
        \in
      \sigma_{N+1}(
        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
        ,M+1
      )
    \)
    for some \(M<\omega\) and thus
    \(
      \alpha
        \in
      \sigma(
        \<C_{N+M+1},C_{N+M+2}\>,
        N+M+2
      )
    \). Thus \(\sigma\) is a winning strategy.
  \end{proof}

  \begin{theorem}
    Let \(\alpha\) be the limit of increasing ordinals \(\beta_n\) for \(n<\omega\).
    If \(\pl F \kmarkwin2\schFillInitialGame{\omega_{\beta_n}}\) for all
    \(n<\omega\), then \(\pl F\kmarkwin2\schFillInitialGame{\omega_\alpha}\).
  \end{theorem}

  \begin{proof}
    Let \(\sigma_n\) be a winning \(2\)-mark for \(\pl F\) in
    \(\schFillInitialGame{\omega_{\beta_n}}\). Define the \(2\)-mark \(\sigma\)
    for \(\pl F\) in \(\schFillInitialGame{\omega_\alpha}\) as follows:
    \[
      \sigma(\<C\>,0)
        =
      \sigma_0(\<C\cap\omega_{\beta_0}\>,0)
    \]
    \[
      \sigma(\<C,D\>,n+1)
        =
      \sigma_{n+1}(\<D\cap\omega_{\beta_{n+1}}\>,0)
        \cup
      \bigcup_{m\leq n}
      \sigma_m(\<C\cap\omega_{\beta_m},D\cap\omega_{\beta_m}\>,n-m+1)
    \]

    Let \(\<C_0,C_1,\dots\>\) be an attack by
    \(\pl C\) in \(\schFillInitialGame{\omega_\alpha}\), and
    \(\alpha\in C_0\).
    Choose \(N<\omega\) with \(\alpha<\omega_{\beta_{N+1}}\). Consider the
    attack
    \(\<C_{N+1}\cap\omega_{\beta_{N+1}},C_{N+2}\cap\omega_{\beta_{N+1}},\dots\>\)
    by \(\pl C\) in \(\schFillInitialGame{\omega_{\beta_{N+1}}}\). Since
    \(\sigma_{N+1}\) is a winning strategy and
    \(\alpha\in C_{N+1}\cap\omega_{\beta_{N+1}}\), either
    \(\alpha\in\sigma_{N+1}(\<C_{N+1}\cap\omega_{\beta_{N+1}}\>,0)\) and thus
    \(\alpha\in\sigma(\<C_N,C_{N+1}\>,N+1)\), or
    \(
      \alpha
        \in
      \sigma_{N+1}(
        \<C_{N+M+1}\cap\omega_{\beta_{N+1}},C_{N+M+2}\cap\omega_{\beta_{N+1}}\>
        ,M+1
      )
    \)
    for some \(M<\omega\) and thus
    \(
      \alpha
        \in
      \sigma(
        \<C_{N+M+1},C_{N+M+2}\>,
        N+M+2
      )
    \). Thus \(\sigma\) is a winning strategy.
  \end{proof}

  \begin{corollary}
    It is consistent that \(S'(\omega_\omega)\) fails,
    but as \(S'(\omega_k)\) holds for all \(k<\omega\), we have
    \(\pl F\kmarkwin2\schFillIntGame{\omega_\omega}\) and
    \(\pl F\kmarkwin2\schFillInitialGame{\omega_\omega}\).
  \end{corollary}

  A tricky topological question: does \(\pl F\win\menGame{X}\) imply
  \(\pl F\kmarkwin2\menGame{X}\)?
  (C showed that )
  Under \(V=L\), we cannot hope to find
  a counterexample using \(X=\oneptlind\kappa\) since
  \(S'(\kappa)\) and thus \(\pl F\kmarkwin2\schFillIntGame{\kappa}\)
  always holds.

  \begin{definition}
    Let \(R_\omega\) be the real numbers with the topology of the usual
    open intervals with countably many elements removed.
  \end{definition}

  \begin{theorem}
    \(\pl F\win\menGame{R_\omega}\).
    If there exists a Kurepa family on the reals, then
    \(\pl F\kmarkwin2\menGame{R_\omega}\).
  \end{theorem}

\end{document}
